\documentclass[../main.tex]{subfiles}
\begin{document}

\begin{question}
    Exercise 4-1: Consider the following stage game.
    \begin{table}[h]
    \centering
\begin{tabular}{lccc}
                            & \multicolumn{1}{l}{Left} & \multicolumn{1}{l}{Middle} & \multicolumn{1}{l}{Right} \\ \hline
\multicolumn{1}{l|}{Left}   & (4, 2)                   & (3, 3)                     & (1, 2)                    \\
\multicolumn{1}{l|}{Middle} & (3, 3)                   & (5, 5)                     & (2, 6)                    \\
\multicolumn{1}{l|}{Right}  & (2, 1)                   & (6, 2)                     & (3, 3)                   
\end{tabular}
\end{table}

\begin{enumerate}
  \item Find the pure-strategy NE (PSNE) of the stage game.
  \item Find the PSNE and subgame perfect NE (SPNE) of the game that consists of the stage game being played twice.
  \item Suppose that the game continues to the next period with probability $p$.What is the threshold $p^*$ such that when $p \geq p^*$, $(M,M)$ is sustainable as a SPNE by grim trigger strategies. Choose the grim trigger strategies so that $p^*$ is minimised.
\end{enumerate}

\end{question}

\begin{solution}

\begin{enumerate}
  \item $(R,R)$
  \item 2 times $(R,R)$
  \item For player 1:
$U_1 (R,M) + \sum\limits_{i=1}^{\infty} p^i 3 \geq \sum\limits_{i=1}^{\infty} U_1 (M,M) p^i$\\
$\Leftrightarrow 6 + \frac{3}{1-p} - 3 \geq \frac{5}{1-p}$\\
$\Leftrightarrow p \leq \frac{1}{3}$

\end{enumerate}

\end{solution}

\begin{question}
Exercise 4-2: \textbf{Deze vraag is verdwenen in de opgave die nu online staat op Toledo, laten we die dan ook weg? (De nummering is ook aangepast zodat vraag 4-3, 4-2 is in de opgave op Toledo)}
\end{question}

\begin{solution}
\end{solution}

\begin{question}

Exercise 4-3: Consider the following stage game.
\begin{table}[h]
\centering
\begin{tabular}{lccc}
                            & \multicolumn{1}{l}{Left} & \multicolumn{1}{l}{Middle} & \multicolumn{1}{l}{Right} \\ \hline
\multicolumn{1}{l|}{Top}    & (1, 1)                   & (5, 0)                     & (0, 0)                    \\
\multicolumn{1}{l|}{Middle} & (0, 5)                   & (4, 4)                     & (0, 0)                    \\
\multicolumn{1}{l|}{Right}  & (0, 0)                   & (0, 0)                     & (3, 3)                   
\end{tabular}
\end{table}

\begin{enumerate}
  \item Find the PSNE of the stage game.
  \item Find the PSNE and SPNE of the game that consists of the stage game being played twice.
  \item Suppose that the game continues to the next period with probability $p$. What is the threshold $p^*$ such that when $p \geq p^*$, $(M,M)$ is sustainable as a SPNE by grim trigger strategies? Choose the grim trigger strategies so that $p^*$ is minimised. Is this a SPNE?
\end{enumerate}

\end{question}

\begin{solution}
\begin{enumerate}
\item $(T,L)$; $(B,R)$

\item
\begin{itemize}
\item Repetitions of stage game NE: $(TT,LL); (BB,RR)$
\item Combinations of stage game NE: $(TB,LR); (BT,RL)$
\item NE with grim triggers: $((M ~ GT_1), (M ~ GT_2))$ if $\delta \geq \frac{1}{3}$ \\
	$GT_1$ : play $M$ if player 2 played $M$ in the first game, otherwise play $T$ (= minmax) \\
	$GT_2$ : play $M$ if player 1 played $M$ in the first game, otherwise play $L$ (= minmax) \\		
	Deviation is profitable if
	$5 + 1 \delta > 4 + 4 \delta \Leftrightarrow 1 > 3 \delta \Leftrightarrow \delta < \frac{1}{3}$
\end{itemize}
TODO: These are obviously PSNE, but which of these are also subgame-perfect (SPNE)?

\item
Maximum punishment for player 1 (by player 2)? \\
$\Rightarrow$ Find minmax value of player 1 \\
$\Rightarrow$ Calculate (mixed strategy) NE of zero-sum game with player 1's payoffs
\begin{table}[h]
\centering
\begin{tabular}{lccc}
                            & \multicolumn{1}{l}{Left} & \multicolumn{1}{l}{Middle} & \multicolumn{1}{l}{Right} \\ \hline
\multicolumn{1}{l|}{Top}    & (1, -1)                  & (5, -5)                    & (0, 0)                    \\
\multicolumn{1}{l|}{Middle} & (0, 0)                   & (4, -4)                    & (0, 0)                    \\
\multicolumn{1}{l|}{Right}  & (0, 0)                   & (0, 0)                     & (3, -3)                   
\end{tabular}
\end{table}

Note that M is weakly dominated by T for player 1, and M is weakly dominated by L for player 2. Both M actions can be eliminated, and the NE of the remaining $2 \times 2$ NFG can be found:
\[
\begin{cases}
-1 p + 0 (1-p) &= 0 p - 3 (1-p) \\
1 q + 0 (1-q)  &= 0 q + 3 (1-q)
\end{cases}
\Rightarrow
\begin{cases}
p  &= \frac{3}{4} \\
q  &= \frac{3}{4}
\end{cases}
\]
	
Player 1's minmax value is his expected payoff when playing this minmax strategy:
\[
1 p q + 3 (1-p) (1-q) = \frac{3}{4}
\]
	
Player 1's deviation from $(M, M)$ is profitable if:
\begin{align*}
5 + \frac{3}{4} \sum\limits_{i=1}^{\infty} p^i &> 4 \sum\limits_{i=0}^{\infty} p^i \\
5 + \frac{3}{4} \left( \frac{1}{1 - p} - 1 \right) &> \frac{4}{1 - p} \\
20 + \frac{3}{1 - p} - 3 &> \frac{16}{1 - p} \\
17 &> \frac{13}{1 - p} \\
p &< \frac{4}{17}
\end{align*}
Since the game is symmetric, this result also applies for a deviation by player 2. \\
$(M, M)$ can therefore be sustained as a NE by grim triggers if $p \geq p^* = \frac{4}{17}$
	
TODO: Is this NE a SPNE?

\end{enumerate}
\end{solution}

\begin{question}
Exercise 4-4:
\end{question}

\begin{solution}
\end{solution}

\begin{question}
Exercise 4-5:
\end{question}

\begin{solution}
\end{solution}

\begin{question}
Exercise 4-6:
\end{question}

\begin{solution}
\end{solution}

\begin{question}
Exercise 4-7:
\end{question}

\begin{solution}
\end{solution}

\begin{question}
Exercise 4-8:
\end{question}

\begin{solution}
\end{solution}

\end{document}

